Future challenges for Research Software Engineering

### 2025-05-17 future_challenges_for_RSEng.tex
state-actors sound a bit too undercover to me. So maybe more specific with who we mean.

\emph{Which challenges will still persist}\\
The workshop participants expect that there will still be budgeting and administrative hurdles to creating
permanent and well-funded RSE teams.
Here it can only be strongly hoped, that, with the recognized importance of research software, state-actors
support the development with a reliable stream of funding.
This would also require a change of culture in research about the acceptance of research software.\\
While we hope that the barrier to researchers diminishes, the workshop participants
still expect some work to do. We hope that the compartmentalisation that occurs will help researchers re-prioritise their workload.
An upcoming challenge will be that, with the emergence of more dedicated RSE units,
networking between them will come into the foreground, because there should be a strong need to share best practices
among institutions with successful RSE Teams.
On a more organisational level, we expect the sharing of models on how to organise different RSEs with different areas of specialist expertise, to fit the different organisational constraints.
After that, organisations will have to come up with updated models for hiring people.
While a standardized RSE Master's degree makes it easier to develop the next generation of practitioners with the necessary technical skills, it will be interesting to see if
RSE are still often hired by word of mouth within an organisation(``I have this PhD here, before their PostDoc they would be a good fit for the RSE department...'' ) or if the RSE Master's degree ensures a hiring process on a more standardised level.

>>>>

\emph{Which challenges will still persist}\\
The workshop participants expect that there will still be budgeting and administrative hurdles to creating
permanent and well-funded RSE teams.
Here it can only be strongly hoped, that, with the recognized importance of research software, research councils and funders
support the development with a reliable stream of funding.
This would also require a change of culture in research about the acceptance of research software.\\
While we hope that the barrier to researchers diminishes, the workshop participants
still expect some work to do. We hope that the compartmentalisation that occurs will help researchers re-prioritise their workload.
An upcoming challenge will be that, with the emergence of more dedicated RSE units,
networking between them will come into the foreground, because there should be a strong need to share best practices
among institutions with successful RSE Teams.
On a more organisational level, we expect the sharing of models on how to organise different RSEs with different areas of specialist expertise, to fit the different organisational constraints.
After that, organisations will have to come up with updated models for hiring people.
While a standardized RSE Master's degree makes it easier to develop the next generation of practitioners with the necessary technical skills, it will be interesting to see if
RSE are still often hired by word of mouth within an organisation(``I have this PhD here, before their PostDoc they would be a good fit for the RSE department...'' ) or if the RSE Master's degree ensures a hiring process on a more standardised level.
